Reliable Inferences from Simply Parameterised Models

### 2012-08-31 ms.tex
Convergence plot in paper
Failure plot in paper
Gregory reference
Figure labels
Approximating the pdf

@@

\section{More Objective Temperature Selection}
\begin{itemize}
\item If we can generate from a prior over complex models, and then fit simple models to each sample, and also generate simulated data from the complex model, we can get an idea of the joint prior over the space of (simple parameters, data)\\
\item Approximate the joint prior over (simple parameters, data) with a tempered version of the old likelihood \\
\item Find the optimal temperature that makes the approximated joint prior as close as possible to the true one.
\end{itemize}

@@

>>>>

\begin{figure*}
\begin{center}
\includegraphics[scale=0.5]{failure.eps}
\caption{\label{failure}}
\end{center}
\end{figure*}

\begin{figure*}
\begin{center}
\includegraphics[scale=0.5]{convergence.eps}
\caption{\label{convergence}}
\end{center}
\end{figure*}

@@

\section{More Objective Temperature Selection}
Suppose the complex model has parameters $\eta$.
The joint prior between the simple model parameters $\theta$ and the data $D$
is given by:
\begin{eqnarray}
q_0(\theta, D).
\end{eqnarray}
We wish to approximate this by another distribution:
\begin{eqnarray}
p_T(\theta, D) &=& p(\theta)\mathcal{L}(\theta; D).
\end{eqnarray}
This approximation will be done by maximising:
\begin{eqnarray}
H(T) &=& -\int p_T(\theta, D) \log q_0(\theta, D) \, d\theta \, dD
\end{eqnarray}

\begin{itemize}
\item If we can generate from a prior over complex models, and then fit simple models to each sample, and also generate simulated data from the complex model, we can get an idea of the joint prior over the space of (simple parameters, data)\\
\item Approximate the joint prior over (simple parameters, data) with a tempered version of the old likelihood \\
\item Find the optimal temperature that makes the approximated joint prior as close as possible to the true one.
\end{itemize}

@@

\bibitem[Gregory(2005)]{gregory} Gregory, P.~C., 2005, 
Bayesian Logical Data Analysis for the Physical Sciences. Cambridge 
University Press.\
